The systems $\LDL$ and $\LDL_*$ are defined over the language $\L$ and $\L_*$, respectively. The system $\LDL$ is defined by the table of rules below, while the system $\LDL_*$ is defined by the same rules, except $L \supset$ and $R \supset$.
\input{dfn/ldl}

\begin{rem}\label{rem:ldl-gstn}
  Notice the differences between $\GSTN$ and $\LDL$. The latter lacks the rules $cut$ and $Lc$, its $Id ^p$ rule is just $Id$, limited to the atomic formulas, and its $LW$ can introduce more than one formula to its conclusion, which is admissible in $\GSTN$ by multiple instances of $Lw$. It also differs in $L \wedge ^n$, $L \vee ^n$, $L \rightarrow ^n$ and $L \supset ^n$, which also have arbitrary number of $\nabla$s on their principal formula, which is distributed over its subformulas in their premises.  
\end{rem}

\begin{rem}
  The system $\LDL$ is \emph{analytic}, in the sense that for all of its rules, all formulas in the premises are subformulas of its conclusion, up to $\nabla$. More percisely, all formulas in the premises are of the form $\nabla^n A$ (for some $n \geq 0$) where $A$ is a subformula of the conclusion.
\end{rem}

A direct consequence of the analyticity of $\LDL$ is that we don't need the rules $L \supset$ and $R \supset$ for proving sequents in the language $\L_*$.

\begin{thm}\label{thm:ldl-cons-ext}
  For any sequent $\Gamma \Rightarrow \Delta$ in the language $\L_*$, if $\LDL \vdash \Gamma \Rightarrow \Delta$ then $\LDL_* \vdash \Gamma \Rightarrow \Delta$.
\end{thm}
\begin{proof}
  Easy, by induction on the proof-tree for in $\LDL$. Notice that the cases for $L \supset$ and $R \supset$ are refuted by the assumption.
\end{proof}

In the rest of this section we are going to show that $\LDL$ and $\GSTN$ are equivalent, i.e. prove exactly the same set of sequents. Hence, proving that the logic $\ldl$ has an analytic system. To reach this aim, we have to show the admissibility of $Id$, $Lc$ and $cut$ from $\GSTN$ in $\LDL$, and the admissibility of $L \wedge ^n$, $L \vee ^n$, $L \rightarrow ^n$ and $L \supset ^n$ in $\GSTN$. We also need some lemmas which facilitate our admissibility proofs.

\input{thm/n-dist}

\input{thm/id-adm}

In order to prove the admissibility of $Lc$, we also need the following \emph{inversion} lemmas for some of the rules of $\LDL$.
\input{thm/inv}

The next theorem shows that the rule $Lc$ from $\GSTN$ is admissible in $\LDL$.
\input{thm/lc-adm}

It remains to show that $cut$ is admissible in $\LDL$.

\begin{thm}\label{thm:cut-adm}
  If $\LDL \vdash \Gamma \Rightarrow A$ and $\LDL \vdash \Sigma, A \Rightarrow \Delta$, then $\LDL \vdash \Gamma, \Sigma \Rightarrow \Delta$.
\end{thm}

We postpone the proof of Theorem \ref{thm:cut-adm} to the next section. Nevertheless, we will use its result to show that $\LDL$ and $\GSTN$ are equivalent, and therefore, share the same logic $\ldl$.

\begin{nota}
  Thanks to Theorems \ref{thm:id-adm}, \ref{thm:lc-adm} and \ref{thm:cut-adm}, from now on, we pretend that the rules $Id$, $Lc$ and $cut$ are available in $\LDL$ as well. Therefore, we use them in the proof-trees in $\LDL$ without any further explanation.
\end{nota}

Now, we are ready to prove the equivalence of two systems.

\input{thm/ldl-eq-gstn}

\begin{cor}
  $\ldl$ is the logic of the system $\LDL$.
\end{cor}

Courtesy of these results and the fact that $\ldl$ is a conservative extension of $\ldl_*$, we have the same result for the systems without the rules $L \supset$ and $R \supset$.

\begin{thm}
  Any sequent $\Gamma \Rightarrow \Delta$ in the language $\L_*$ is provable in $\GSTN_*$ iff it is provable in $\LDL_*$.
\end{thm}
\begin{proof}
  Obviously, a proof-tree in $\GSTN_*$ or $\LDL_*$ is also a proof-tree in $\GSTN$ and $\LDL$, respectively. Use Theorem \ref{thm:ldl-eq-gstn} to translate proof-trees between $\GSTN$ and $\LDL$, then use Theorems \ref{thm:gstn-cons-ext} or \ref{thm:ldl-cons-ext} to translate proof-trees to $\LDL_*$ or $\GSTN_*$.
\end{proof}

So we can say the same about $\ldl_*$.

\begin{cor}
  $\ldl_*$ is the logic of the system $\LDL_*$.
\end{cor}